---
author: "Colin Donald"
date: "`r format(Sys.Date(), '%m/%d/%Y')`"
output: 
  word_document: 
    fig_caption: yes
    keep_md: yes
    reference_docx: N:/Status_and_Trend_Reports/Report_Files/Report_Template.docx
    toc: yes
    fig_width: 12
    fig_height: 6
  html_document:
    mode: selfcontained
    number_sections: yes
    template: N:/Status_and_Trend_Reports/Report_Files/report_template.html
    toc: yes
    toc_depth: 5
    toc_float: 
      collapsed: true
      smooth_scroll: true
    fig_width: 12
    fig_height: 6
  pdf_document:
    toc: yes
always_allow_html: yes
---

```{r setup, include=FALSE}

options(knitr.duplicate.label = 'allow')
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning=FALSE,
                      error = FALSE,
                      cache = FALSE,
                      include = TRUE,
                      fig.keep='all',
                      fig.path=paste0(out_dir, "/Figures/"),
                      fig.width = 12, 
                      fig.height = 6)


project_dir <- paste0('N:/Status_and_Trend_Reports/2019/2019-', name, '/')

load(file = paste0(project_dir, name, "_eval_date.RData"))
load(paste0(project_dir, name, "_param_summary_by_station.RData"))
param_sum <- param_sum_stn
load(paste0(project_dir, name, "_param_summary_by_au.RData"))
param_sum <- param_sum %>% dplyr::filter(!is.na(AU_ID))
param_sum <- param_sum %>% dplyr::filter(AU_ID != "")
param_sum$Char_Name <- AWQMS_to_standard(param_sum$Char_Name)
param_sum_au <- param_sum_au %>% dplyr::filter(!is.na(AU_ID))
param_sum_au <- param_sum_au %>% dplyr::filter(AU_ID != "")
param_sum_au$Char_Name <- AWQMS_to_standard(param_sum_au$Char_Name)
status_current <- as.symbol(colnames(param_sum)[grep("trend", colnames(param_sum)) - 1])

area <- readOGR(dsn = 'N:/Status_and_Trend_Reports/GIS', layer = 'Report_Units_HUC08', integer64="warn.loss", verbose = FALSE, stringsAsFactors = FALSE)
area <- area[area$REPORT %in% c(name), ]
area <- sf::st_as_sf(area)
area <- st_transform(area, 4326)

wql_streams <- sf::st_read(
  dsn = "//deqhq1/WQNPS/Agriculture/Status_and_Trend_Analysis/R_support_files",
  layer = "WQL_Streams_2012",
  query = paste0("SELECT * FROM WQL_Streams_2012 WHERE HUC_4TH_CO IN ('",
                 paste(unique(param_sum$HUC8), collapse = "', '"), "')"),
  stringsAsFactors = FALSE, quiet = TRUE
)
wql_streams$Char_Name <- unlist(sapply(wql_streams$POLLUTANT, AWQMS_Char_Names, USE.NAMES = FALSE))
wql_streams$Char_Name <- AWQMS_to_standard(wql_streams$Char_Name)
wql_streams <- sf::st_zm(wql_streams, what = "ZM")
wql_streams <- st_transform(wql_streams, 4326)
wql_streams <- filter(wql_streams[, c("STREAM_NAM", "SEGMENT_ID", "SEASON", "Char_Name", "LISTING_ST", "TMDL_INFO")], Char_Name %in% unique(param_sum$Char_Name))
wql_streams <- wql_streams[lapply(wql_streams$`_ogr_geometry_`, length) != 0,]

if(!dir.exists(paste0(project_dir, "/Maps"))) {dir.create(paste0(project_dir, "/Maps"))}

```

```{=openxml}
<w:p>
</w:pPr>
<w:r>
<w:br w:type="page"/>
</w:r>
</w:p>
```

## `r name` Basin

A summary of status and trend results for the `r name` Basin and subbasins within the `r name` Basin are presented in this section. Full tabular results including results for each station, assessment unit, excursion statistics, and the summary of the OWRI watershed restoration or protection treatments implemented are provided in **Appendix `r a.letter`**.

```{r basinIntro, include = TRUE, results = 'asis'}
wql_data <- read.csv('//deqhq1/WQNPS/Status_and_Trend_Reports/Lookups_Statewide/wq_limited_2012_df_temp_bact_ph_DO_TP_Sediment.csv',
                     stringsAsFactors = FALSE)

param_sum <- param_sum[,c("AU_Name", colnames(param_sum)[colnames(param_sum) != "AU_Name"])]
param_sum$AU_Type <- if_else(grepl("_SR_", param_sum$AU_ID),
                             "Stream",
                             if_else(grepl("_LK_", param_sum$AU_ID),
                                     "Lake",
                                     if_else(grepl("_WS_", param_sum$AU_ID),
                                             "Watershed Unit",
                                             if_else(grepl("_EB_", param_sum$AU_ID),
                                                     "Estuary or Bay",
                                                     if_else(grepl("_CL_", param_sum$AU_ID),
                                                             "Coastline",
                                                             NA_character_
                                                     )
                                             )
                                     )
                             )
)
param_sum_au$AU_Type <- if_else(grepl("_SR_", param_sum_au$AU_ID),
                                "Stream",
                                if_else(grepl("_LK_", param_sum_au$AU_ID),
                                        "Lake",
                                        if_else(grepl("_WS_", param_sum_au$AU_ID),
                                                "Watershed Unit",
                                                if_else(grepl("_EB_", param_sum_au$AU_ID),
                                                        "Estuary or Bay",
                                                        if_else(grepl("_CL_", param_sum_au$AU_ID),
                                                                "Coastline",
                                                                NA_character_
                                                        )
                                                )
                                        )
                                )
)
param_sum[param_sum$AU_ID == "Sru Lake", c("AU_Name", "AU_Type")] <- c("Sru Lake", "Lake")
param_sum_au[param_sum_au$AU_ID == "Sru Lake", c("AU_Name", "AU_Type")] <- c("Sru Lake", "Lake")

param_sum <- param_sum %>% dplyr::rename(Pollutant = Char_Name, Station_Description = StationDes)

simpleCap <- function(x) {
  s <- strsplit(x, " ")[[1]]
  paste(toupper(substring(s, 1,1)), substring(s, 2),
        sep="", collapse=" ")
}

types <- unique(param_sum_au$AU_Type)
n_types <- length(unique(param_sum_au$AU_Type))
parameters <- odeqstatusandtrends::AWQMS_to_standard(unique(param_sum_au$Char_Name))
n_params <- length(unique(param_sum_au$Char_Name))
list_fun <- function(x){paste(x, collapse = "s', '")}
param_summary <- unique(param_sum$Pollutant)

cat("\n\n")

cat(paste0("The ", name, " basin is listed for ", length(unique(wql_data$POLLUTANT)), " parameters among its water bodies. Available data were sufficient to assess status and/or trend at ", length(unique(param_sum$MLocID)), " stations within the ", name, " basin. These stations were located across ", length(unique(param_sum_au$AU_ID)), " assessment units consisting of '", list_fun(types[1:(n_types - 1)]), "s' and '", list_fun(types[n_types]), "s'. Data for ", 
           gsub("'", "", 
                paste0(paste(parameters[1:(n_params - 1)], collapse = "', '"), "' and '", paste(parameters[n_params], collapse = "', '")
                       , "'")
           ), " were available for analysis and included in this report.\n\n"))
```


```{r landuse, include = FALSE, results = 'asis', eval=TRUE, fig.height=7}

landuse_output <- NULL

landuse_output <- knitr::knit_child("state_landuse_summary.Rmd", envir = globalenv())

```

`r paste(landuse_output, collapse = "\n")`

```{r basinStatus, include = TRUE, results = 'asis', fig.height=6, fig.cap = cap_list, eval.after = 'fig.cap'}

cap_list <- list()

cat("### Parameter Maps\n\n")

cat(paste("The maps in ", figs(paste0(name, "_", param_summary[1], "_map"), display = 'cite')," through ", figs(paste0(name, "_", param_summary[length(param_summary)], "_map"), display = 'cite')," show the stations included in the analysis for each parameter. Stations are color coded by current status. The water quality listed streams for each parameter are included in the maps as red lines."), "\n\n")

for(i in unique(param_sum$Pollutant)){
  if(i != "pH"){
    parameter_name <- simpleCap(i)
  } else {parameter_name <- "pH"}
  
  if(!file.exists(paste0(project_dir, "/Maps/", gsub(",| ", "_", i), ".png"))){
    wql_streams_i <- filter(wql_streams[, c("STREAM_NAM", "SEGMENT_ID", "SEASON", "Char_Name", "LISTING_ST", "TMDL_INFO")], Char_Name == i)
    wql_streams_i <- wql_streams_i[lapply(wql_streams_i$`_ogr_geometry_`, length) != 0,]
    
    map_df <- param_sum %>% filter(Pollutant == i) %>% mutate(color = if_else(!!status_current %in% c("Unassessed", "Insufficient Data"),
                                                                              "lightgray",
                                                                              if_else(!!status_current == "Not Attaining",
                                                                                      "orange",
                                                                                      "green")
    ))
    
    map <- leaflet(map_df, options = leafletOptions(zoomControl = FALSE)) %>% 
      addProviderTiles("Esri.NatGeoWorldMap") %>% 
      addPolylines(data = wql_streams_i,
                   opacity = 1,
                   weight = 2,
                   color = "red",
                   smoothFactor = 2,
                   group = "WQ Listed Streams"
      ) %>% 
      addPolygons(data = area, fill = FALSE, group = "Basin", opacity = 1, weight = 3, color = "black", label = paste(name, "Basin")) %>%
      addCircleMarkers(lng = ~Long_DD, lat = ~Lat_DD, fillColor = ~color, stroke = TRUE, weight = 1, 
                       opacity = 1, fillOpacity = 1, color = 'black', radius = 4.5, label = ~color) %>% 
      addControl(position = "bottomright", className = "legend",
                 html = sprintf('<html><body><div style="opacity:0.95">
                                        <img width="175" height="150" src="data:image/png;base64,%s">
                            </div></body></html>', lgnd)) %>% 
      addControl(html = paste('<div style="opacity:0.95; background:white; padding:0px 6px; border-radius: 8px; font-size:18px"><b>', 
                              name, parameter_name, "Status</b></div>"), 
                 position = "topleft", className = "map_title")
    
    mapview::mapshot(map, file = paste0(project_dir, "/Maps/", gsub(",| ", "_", i), ".png")
                     , selfcontained = FALSE)
  }
  
  cat(paste0("![", 
             figs(name = paste0(name, "_", i, "_map"), caption = paste0("Summary map of the status of ", i, " across the ", name, " Basin.")),
             "](", project_dir, "/Maps/", gsub(",| ", "_", i), ".png)"), "\n")
  
  cat("\n\n")
}

cat("### Status\n\n")

cat(paste0(tbls(name = paste0(name, "_au_sum"), display = 'cite'), " shows the number of attaining, not attaining, and unassessed assessment units by parameter.\n\n"))

au_sum <- param_sum_au %>% group_by(Char_Name) %>% 
  summarise(Attaining = sum(status_2015_2018 == "Attaining"),
            'Not Attaining' = sum(status_2015_2018 == "Not Attaining"),
            Unassessed = sum(status_2015_2018 == "Unassessed")) %>% 
  mutate(Char_Name = sapply(Char_Name, simpleCap, USE.NAMES = FALSE)) %>% 
  rename(Pollutant = Char_Name)

knitr::kable(au_sum, padding = 0, digits = 1, row.names = FALSE, format = table_format,
             caption = tbls(name = paste0(name, "_au_sum"), caption = paste0("Summary of assessment unit status within the ", name, " Basin."))
) %>% table_style()

cat("\n\n")

ggplot(reshape2::melt(au_sum, id.vars = "Pollutant", variable.name = "Status"))+
  geom_bar(aes(x = Pollutant, y = value, fill = Status), stat = "identity", position = "dodge")+
  xlab("Pollutant")+
  ylab("# of Assessment Units")+
  scale_fill_manual(values = c("Attaining" = "forestgreen", "Not Attaining" = "orange", "Unassessed" = "gray"))+
  theme_bw()+
  ggtitle("Assessment Unit Attainment Count", subtitle = "Summarized by Pollutant")

cap_list[[1]] <- figs(name = paste0(name, "_au_sum_plot"), caption = paste0("Summary plot of assessment unit status within the ", name, " Basin by parameter."))

cat(paste0("\n\n",tbls(name = paste0(name, "_au_type_sum"), display = 'cite')," and ", figs(name = paste0(name, "_au_sum_plot"), display = 'cite')," summarizes the number of attaining, not attaining, and unassessed assessment units by parameter and assessment unit type within the ", name," Basin.\n\n"))

au_sum_type <- param_sum_au %>% group_by(AU_Type, Char_Name) %>% 
  summarise(Attaining = sum(status_2015_2018 == "Attaining"),
            "Not Attaining" = sum(status_2015_2018 == "Not Attaining"),
            Unassessed = sum(status_2015_2018 == "Unassessed")) %>% 
  mutate(Char_Name = sapply(Char_Name, simpleCap, USE.NAMES = FALSE)) %>% 
  rename("AU Type" = AU_Type, Pollutant = Char_Name)

knitr::kable(au_sum_type, padding = 0, digits = 1, row.names = FALSE, format = table_format
             ,
             caption = tbls(name = paste0(name, "_au_type_sum"), caption = paste0(name, " Basin status summary of assessment units by type."))
) %>% table_style()


cat("\n\n")

cat(paste0("\n\n", tbls(name = paste0(name, "_stn_sum"), display = 'cite')," and ", figs(name = paste0(name, "_stn_sum_plot"), display = 'cite')," summarizes the number of attaining, not attaining, and unassessed stations by parameter.\n\n"))

stn_sum <- param_sum %>% group_by(Pollutant) %>% 
  summarise(Attaining = sum(status_2015_2018 == "Attaining"),
            "Not Attaining" = sum(status_2015_2018 == "Not Attaining"),
            Unassessed = sum(status_2015_2018 == "Unassessed")) %>% 
  mutate(Pollutant = sapply(Pollutant, simpleCap, USE.NAMES = FALSE))

knitr::kable(stn_sum, padding = 0, digits = 1, row.names = FALSE, format = table_format
             ,
             caption = tbls(name = paste0(name, "_stn_sum"), caption = paste0("Summary of the status of stations within the ", name, " Basin."))
) %>% table_style()

cat("\n\n")

ggplot(reshape2::melt(stn_sum, id.vars = "Pollutant", variable.name = "Status"))+
  geom_bar(aes(x = Pollutant, y = value, fill = Status), stat = "identity", position = "dodge")+
  xlab("Pollutant")+
  ylab("# of Stations")+
  scale_fill_manual(values = c("Attaining" = "forestgreen", "Not Attaining" = "orange", "Unassessed" = "gray"))+
  theme_bw()+
  ggtitle("Station Attainment Count", subtitle = "Summarized by Pollutant")

cap_list[[2]] <- figs(name = paste0(name, "_stn_sum_plot"), caption = paste0("Summary plot of station status within the ", name, " Basin by parameter."))

cat("\n\n")
cat("### Trend\n\n")

cat(paste0("\n\nA summary of the trends across parameters is shown in ",tbls(name = paste0(name, "_stn_trend_sum"), display="cite"),". Note that trend requires significantly more data than status and may result in many stations with sufficient data for assessing status, but insufficient data for assessing trend.\n\n"))

stn_sum <- param_sum %>% group_by(Pollutant) %>% 
  summarise(Improving = sum(trend == "Improving"),
            Degrading = sum(trend == "Degrading"),
            Steady = sum(trend == "Steady"),
            "No Significant Trend" = sum(trend == "No Significant Trend"),
            "Insufficient Data" = sum(trend == "Insufficient Data"),
  ) %>% 
  mutate(Pollutant = sapply(Pollutant, simpleCap, USE.NAMES = FALSE))

knitr::kable(stn_sum, padding = 0, digits = 1, row.names = FALSE, format = table_format
             ,
             caption = tbls(name = paste0(name, "_stn_trend_sum"), caption = paste0(name, " Basin summary of trends at stations across the state."))
) %>% table_style()

cat("\n\n")

```

### Subbasin Summary

```{r subbasin, include = FALSE, eval=TRUE, results = 'asis'}

subbasin_output <- NULL

capnum <- 3

for(i in unique(param_sum$HUC8)){
  
  data <- param_sum %>% dplyr::filter(HUC8 == i)
  map_df <- data
  par_sum <- data %>% dplyr::select(-Lat_DD, -Long_DD, -HUC8, -HUC8_Name)
  par_sum_au <- param_sum_au %>% filter(AU_ID %in% data$AU_ID)
  
  subbasin_name <- huc_names[huc_names$HUC8 == i,]$HUC8_Name
  sub_area <- area[area$HUC_8 == i,]
  
  subbasin_output <- c(subbasin_output, knitr::knit_child("state_subbasin_summary.Rmd", envir = globalenv()))
  
  capnum <- as.numeric(capnum)
  
  print(capnum)
  
}

```

`r paste(subbasin_output, collapse = '\n')`
