---
author: "Colin Donald"
date: "`r format(Sys.Date(), '%m/%d/%Y')`"
output: 
  word_document: 
    fig_caption: yes
    keep_md: yes
    reference_docx: N:/Status_and_Trend_Reports/Report_Files/Report_Template.docx
    toc: yes
    fig_width: 12
    fig_height: 6
  html_document:
    mode: selfcontained
    number_sections: yes
    template: N:/Status_and_Trend_Reports/Report_Files/report_template.html
    toc: yes
    toc_depth: 5
    toc_float: 
      collapsed: true
      smooth_scroll: true
    fig_width: 12
    fig_height: 6
  pdf_document:
    toc: yes
always_allow_html: yes
---

```{r setup, include=FALSE}

options(knitr.duplicate.label = 'allow')
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning=FALSE,
                      error = FALSE,
                      cache = FALSE,
                      include = TRUE,
                      fig.keep='all',
                      fig.path=paste0(out_dir, "/Figures/"),
                      fig.width = 12, 
                      fig.height = 6)


project_dir <- paste0(top_dir, '2020-', name, '/')

load(file = paste0(project_dir, name, "_eval_date.RData"))
load(paste0(project_dir, name, "_param_summary_by_station.RData"))
param_sum <- param_sum_stn
load(paste0(project_dir, name, "_param_summary_by_au.RData"))
param_sum <- param_sum %>% dplyr::filter(!is.na(AU_ID))
param_sum <- param_sum %>% dplyr::filter(AU_ID != "")
param_sum$Char_Name <- odeqstatusandtrends::AWQMS_to_standard(param_sum$Char_Name)
param_sum_au <- param_sum_au %>% dplyr::filter(!is.na(AU_ID))
param_sum_au <- param_sum_au %>% dplyr::filter(AU_ID != "")
param_sum_au$Char_Name <- odeqstatusandtrends::AWQMS_to_standard(param_sum_au$Char_Name)
status_current <- as.symbol(colnames(param_sum)[grep("trend", colnames(param_sum)) - 1])

area <- rgdal::readOGR(dsn = 'N:/Status_and_Trend_Reports/GIS', layer = 'Report_Units_HUC08', integer64="warn.loss", verbose = FALSE, stringsAsFactors = FALSE)
area <- area[area$REPORT %in% c(name), ]
area <- sf::st_as_sf(area)
area <- sf::st_transform(area, 4326)

# wql_streams <- sf::st_read(
#   dsn = "//deqhq1/WQNPS/Agriculture/Status_and_Trend_Analysis/R_support_files",
#   layer = "WQL_Streams_2012",
#   query = paste0("SELECT * FROM WQL_Streams_2012 WHERE HUC_4TH_CO IN ('",
#                  paste(unique(param_sum$HUC8), collapse = "', '"), "')"),
#   stringsAsFactors = FALSE, quiet = TRUE
# )
# wql_streams$Char_Name <- unlist(sapply(wql_streams$POLLUTANT, AWQMS_Char_Names, USE.NAMES = FALSE))
# wql_streams$Char_Name <- odeqstatusandtrends::AWQMS_to_standard(wql_streams$Char_Name)
# wql_streams <- sf::st_zm(wql_streams, what = "ZM")
# wql_streams <- sf::st_transform(wql_streams, 4326)
# wql_streams <- dplyr::filter(wql_streams[, c("STREAM_NAM", "SEGMENT_ID", "SEASON", "Char_Name", "LISTING_ST", "TMDL_INFO")], Char_Name %in% unique(param_sum$Char_Name))
# wql_streams <- wql_streams[lapply(wql_streams$`_ogr_geometry_`, length) != 0,]
basin_12s <- hucs[hucs$HUC_8 %in% unique(param_sum$HUC8),]$HUC_12

if(name == "Columbia River"){
  
  columbia_aus <- sf::st_read(
    dsn = "//deqhq1/wqnps/Status_and_Trend_Reports/GIS/Assessment_Units.gdb",
    layer = "Columbia_River", quiet = TRUE
  )$AU_ID
  
  basin_wql_streams_lines <- sf::st_read(
    dsn = "//deqhq1/GISLIBRARY/Base_Data/DEQ_Data/Water_Quality/WQ_2018_IntegratedReport/WQ_Assessment_2018_20.gdb",
    layer = "Impaired_Pollutant_Rivers_Coast",
    query = paste0("SELECT * FROM Impaired_Pollutant_Rivers_Coast WHERE AU_ID IN ('",
                   paste(columbia_aus, collapse = "', '"), "')"),
    stringsAsFactors = FALSE
  )
  basin_wql_streams_ws <- sf::st_read(
    dsn = "//deqhq1/GISLIBRARY/Base_Data/DEQ_Data/Water_Quality/WQ_2018_IntegratedReport/WQ_Assessment_2018_20.gdb",
    layer = "Impaired_Pollutant_Watershed",
    query = paste0("SELECT * FROM Impaired_Pollutant_Watershed WHERE AU_ID IN ('",
                   paste(columbia_aus, collapse = "', '"), "')"),
    stringsAsFactors = FALSE
  )
  
} else if(name == "Snake River"){
  
  snake_aus <- c(
    sf::st_read(
      dsn = "//deqhq1/wqnps/Status_and_Trend_Reports/GIS/Assessment_Units.gdb",
      layer = "Snake_River_Lines", quiet = TRUE)$AU_ID,
    sf::st_read(
      dsn = "//deqhq1/wqnps/Status_and_Trend_Reports/GIS/Assessment_Units.gdb",
      layer = "Snake_River_waterbodies", quiet = TRUE)$AU_ID,
    sf::st_read(
      dsn = "//deqhq1/wqnps/Status_and_Trend_Reports/GIS/Assessment_Units.gdb",
      layer = "Snake_River_Watershed", quiet = TRUE)$AU_ID
  )
  
  basin_wql_streams_lines <- sf::st_read(
    dsn = "//deqhq1/GISLIBRARY/Base_Data/DEQ_Data/Water_Quality/WQ_2018_IntegratedReport/WQ_Assessment_2018_20.gdb",
    layer = "Impaired_Pollutant_Rivers_Coast",
    query = paste0("SELECT * FROM Impaired_Pollutant_Rivers_Coast WHERE AU_ID IN ('",
                   paste(snake_aus, collapse = "', '"), "')"),
    stringsAsFactors = FALSE
  )
  basin_wql_streams_ws <- sf::st_read(
    dsn = "//deqhq1/GISLIBRARY/Base_Data/DEQ_Data/Water_Quality/WQ_2018_IntegratedReport/WQ_Assessment_2018_20.gdb",
    layer = "Impaired_Pollutant_Watershed",
    query = paste0("SELECT * FROM Impaired_Pollutant_Watershed WHERE AU_ID IN ('",
                   paste(snake_aus, collapse = "', '"), "')"),
    stringsAsFactors = FALSE
  )
  
} else {
  basin_wql_streams_lines <- sf::st_read(
    dsn = "//deqhq1/GISLIBRARY/Base_Data/DEQ_Data/Water_Quality/WQ_2018_IntegratedReport/WQ_Assessment_2018_20.gdb",
    layer = "Impaired_Pollutant_Rivers_Coast",
    query = paste0("SELECT * FROM Impaired_Pollutant_Rivers_Coast WHERE HUC12 IN ('",
                   paste(basin_12s, collapse = "', '"), "')"),
    stringsAsFactors = FALSE
  )
  basin_wql_streams_ws <- sf::st_read(
    dsn = "//deqhq1/GISLIBRARY/Base_Data/DEQ_Data/Water_Quality/WQ_2018_IntegratedReport/WQ_Assessment_2018_20.gdb",
    layer = "Impaired_Pollutant_Watershed",
    query = paste0("SELECT * FROM Impaired_Pollutant_Watershed WHERE HUC12 IN ('",
                   paste(basin_12s, collapse = "', '"), "')"),
    stringsAsFactors = FALSE
  )
}

if(NROW(basin_wql_streams_lines) > 0){
  basin_wql_streams_lines$Char_Name <- unlist(sapply(basin_wql_streams_lines$Char_Name, AWQMS_Char_Names, USE.NAMES = FALSE))
  basin_wql_streams_lines$Char_Name <- odeqstatusandtrends::AWQMS_to_standard(basin_wql_streams_lines$Char_Name)
  
} else if(NROW(basin_wql_streams_ws) > 0){
  basin_wql_streams_ws$Char_Name <- unlist(sapply(basin_wql_streams_ws$Char_Name, AWQMS_Char_Names, USE.NAMES = FALSE))
  basin_wql_streams_ws$Char_Name <- odeqstatusandtrends::AWQMS_to_standard(basin_wql_streams_ws$Char_Name)
  
}

basin_wql_streams_lines <- sf::st_zm(basin_wql_streams_lines, what = "ZM")
basin_wql_streams_ws <- sf::st_zm(basin_wql_streams_ws, what = "ZM")

basin_wql_streams_lines <- st_transform(basin_wql_streams_lines, 4326)
basin_wql_streams_lines <- dplyr::filter(basin_wql_streams_lines[, c("AU_Name", "AU_ID", "Period", "Char_Name", "IR_category")],
                                         Char_Name %in% unique(param_sum$Char_Name))

basin_wql_streams_ws <- st_transform(basin_wql_streams_ws, 4326)
basin_wql_streams_ws <- dplyr::filter(basin_wql_streams_ws[, c("AU_Name", "AU_ID", "Period", "Char_Name", "IR_category")],
                                      Char_Name %in% unique(param_sum$Char_Name))

# basin_wql_streams_lines_shp <- basin_wql_streams_lines %>% dplyr::group_by(Char_Name) %>% dplyr::summarise(Shape = sf::st_union(Shape))
# basin_wql_streams_ws_shp <- basin_wql_streams_ws %>% dplyr::group_by(Char_Name) %>% dplyr::summarise(Shape = sf::st_union(Shape))

if(!dir.exists(paste0(project_dir, "/Maps"))) {dir.create(paste0(project_dir, "/Maps"))}

```

```{=openxml}
<w:p>
</w:pPr>
<w:r>
<w:br w:type="page"/>
</w:r>
</w:p>
```

## `r name`

A summary of status and trend results for the `r name` and all subbasins within the `r name` are presented in this section. Full tabular results including results for each station, assessment unit, excursion statistics, and the summary of the OWRI watershed restoration or protection treatments implemented are provided in **Appendix `r a.letter`**.

```{r basinIntro, include = TRUE, results = 'asis'}
wql_data <- read.csv('//deqhq1/WQNPS/Status_and_Trend_Reports/Lookups_Statewide/WQL_assessment_units.csv',
                     stringsAsFactors = FALSE)

if(name == "Columbia River"){
  
  wql_data <- wql_data %>% dplyr::filter(AU_ID %in% columbia_aus, 
                                         Char_Name %in% odeqstatusandtrends::AWQMS_Char_Names(c("tp", "pH", "temperature", "bacteria", "tss", "do")))
  
} else if(name == "Snake River"){
  
  wql_data <- wql_data %>% dplyr::filter(AU_ID %in% snake_aus, 
                                         Char_Name %in% odeqstatusandtrends::AWQMS_Char_Names(c("tp", "pH", "temperature", "bacteria", "tss", "do")))
  
} else {wql_data <- wql_data %>% dplyr::filter(HUC12 %in% basin_12s, 
                                         Char_Name %in% odeqstatusandtrends::AWQMS_Char_Names(c("tp", "pH", "temperature", "bacteria", "tss", "do")))}

param_sum <- param_sum[,c("AU_Name", colnames(param_sum)[colnames(param_sum) != "AU_Name"])]
param_sum$AU_Type <- dplyr::if_else(grepl("_SR_", param_sum$AU_ID),
                                    "Stream",
                                    dplyr::if_else(grepl("_LK_", param_sum$AU_ID),
                                                   "Lake",
                                                   dplyr::if_else(grepl("_WS_", param_sum$AU_ID),
                                                                  "Watershed Unit",
                                                                  dplyr::if_else(grepl("_EB_", param_sum$AU_ID),
                                                                                 "Estuary or Bay",
                                                                                 dplyr::if_else(grepl("_CL_", param_sum$AU_ID),
                                                                                                "Coastline",
                                                                                                NA_character_
                                                                                 )
                                                                  )
                                                   )
                                    )
)
param_sum_au$AU_Type <- dplyr::if_else(grepl("_SR_", param_sum_au$AU_ID),
                                       "Stream",
                                       dplyr::if_else(grepl("_LK_", param_sum_au$AU_ID),
                                                      "Lake",
                                                      dplyr::if_else(grepl("_WS_", param_sum_au$AU_ID),
                                                                     "Watershed Unit",
                                                                     dplyr::if_else(grepl("_EB_", param_sum_au$AU_ID),
                                                                                    "Estuary or Bay",
                                                                                    dplyr::if_else(grepl("_CL_", param_sum_au$AU_ID),
                                                                                                   "Coastline",
                                                                                                   NA_character_
                                                                                    )
                                                                     )
                                                      )
                                       )
)
param_sum[param_sum$AU_ID == "Sru Lake", c("AU_Name", "AU_Type")] <- c("Sru Lake", "Lake")
param_sum_au[param_sum_au$AU_ID == "Sru Lake", c("AU_Name", "AU_Type")] <- c("Sru Lake", "Lake")

param_sum <- param_sum %>% dplyr::rename(Pollutant = Char_Name, Station_Description = StationDes)

simpleCap <- function(x) {
  s <- strsplit(x, " ")[[1]]
  paste(toupper(substring(s, 1,1)), substring(s, 2),
        sep="", collapse=" ")
}

types <- unique(param_sum_au$AU_Type)
n_types <- length(unique(param_sum_au$AU_Type))
parameters <- odeqstatusandtrends::AWQMS_to_standard(unique(param_sum_au$Char_Name))
n_params <- length(unique(param_sum_au$Char_Name))
list_fun <- function(x){paste(x, collapse = "s', '")}
param_summary <- unique(param_sum$Pollutant)

cat("\n\n")

cat(paste0("Based the 2018/2020 303(d)/305(b) Integrated Report (DEQ, 2020), assessment units in the ", name, " are water quality limited for ", length(unique(wql_data$Char_Name)), " parameters out of the six parameters assessed in this report. Available data were sufficient to assess status and/or trend at ", length(unique(param_sum$MLocID)), " stations within the ", name, ". These stations were located across ", length(unique(param_sum_au$AU_ID)), " assessment units consisting of '", list_fun(types[1:(n_types - 1)]), "s' and '", list_fun(types[n_types]), "s'. Data for ",
           gsub("'", "", 
                paste0(paste(parameters[1:(n_params - 1)], collapse = "', '"), "' and '", paste(parameters[n_params], collapse = "', '")
                       , "'")
           ), " were available for analysis and included in this report.\n\n"))
```


```{r landuse, include = FALSE, results = 'asis', eval=TRUE, fig.height=7}

landuse_output <- NULL

landuse_output <- knitr::knit_child("state_landuse_summary.Rmd", envir = globalenv())

```

`r paste(landuse_output, collapse = "\n")`

### Parameter Maps


```{r caps, include = FALSE}
for(i in param_summary){
  if(i != "pH"){
    parameter_name <- simpleCap(i)
  } else {parameter_name <- "pH"}
  figs(name = paste0(name, "_", i, "_map"), caption = paste0("Summary map of the status of ", i, " across the ", name, "."))
}
```


`r paste("The maps in ", figs(paste0(name, "_", param_summary[1], "_map"), display = 'cite')," through ", figs(paste0(name, "_", param_summary[length(param_summary)], "_map"), display = 'cite')," show the stations included in the analysis for each parameter. Stations are color coded by the `r paste(complete_years[17], "–", complete_years[20])` status. The water quality listed streams for each parameter are included in the maps as pink lines.")`


```{r basinStatus, include = TRUE, results = 'asis', fig.height=6, fig.cap = cap_list, eval.after = 'fig.cap'}

cap_list <- list()

for(i in param_summary){
  if(i != "pH"){
    parameter_name <- simpleCap(i)
  } else {parameter_name <- "pH"}
  
  if(!file.exists(paste0(project_dir, "/Maps/", gsub(",| ", "_", i), ".png"))){
    
    basin_wql_streams_lines_i <- dplyr::filter(basin_wql_streams_lines, Char_Name == i)
    basin_wql_streams_ws_i <- dplyr::filter(basin_wql_streams_ws, Char_Name == i)
    
    map_df <- param_sum %>% dplyr::filter(Pollutant == i) %>% dplyr::mutate(color = dplyr::if_else(!!status_current %in% c("Unassessed", "Insufficient Data"),
                                                                                                   "lightgray",
                                                                                                   dplyr::if_else(!!status_current == "Not Attaining",
                                                                                                                  "orange",
                                                                                                                  "green")
    ))
    
    map <- leaflet::leaflet(map_df, options = leaflet::leafletOptions(zoomControl = FALSE)) %>% 
      leaflet::addProviderTiles("Esri.NatGeoWorldMap") %>% 
      leaflet::addPolygons(data = basin_wql_streams_ws_i,
                            opacity = 1,
                            weight = 2,
                            color = "#ff33be",
                           fillOpacity = 0.1,
                           fillColor = "#ff33be",
                           group = "WQ Listed Streams") %>% 
      leaflet::addPolylines(data = basin_wql_streams_lines_i,
                            opacity = 1,
                            weight = 2,
                            color = "#ff33be",
                            smoothFactor = 2,
                            group = "WQ Listed Streams"
      ) %>% 
      leaflet::addPolygons(data = area, fill = FALSE, group = "Basin", opacity = 1, weight = 3, color = "black", label = paste(name, "Basin")) %>%
      leaflet::addCircleMarkers(lng = ~Long_DD, lat = ~Lat_DD, fillColor = ~color, stroke = TRUE, weight = 1, 
                                opacity = 1, fillOpacity = 1, color = 'black', radius = 4.5, label = ~color) %>% 
      leaflet::addControl(position = "bottomright", className = "legend",
                          html = sprintf('<html><body><div style="opacity:0.95">
                                        <img width="175" height="150" src="data:image/png;base64,%s">
                            </div></body></html>', lgnd)) %>% 
      leaflet::addControl(html = paste('<div style="opacity:0.95; background:white; padding:0px 6px; border-radius: 8px; font-size:18px"><b>', 
                                       name, parameter_name, "Status</b></div>"), 
                          position = "topleft", className = "map_title")
    
    mapview::mapshot(map, file = paste0(project_dir, "/Maps/", gsub(",| ", "_", i), ".png")
                     , selfcontained = FALSE)
  }
  
  cat(paste0("![",
             # figs(name = paste0(name, "_", i, "_map"), caption = paste0("Summary map of the status of ", i, " across the ", name, " Basin.")),
             figs(name = paste0(name, "_", i, "_map")),
             "](", project_dir, "Maps/", gsub(",| ", "_", i), ".png)"), "\n")
  
  cat("\n\n")
}

cat("### Status\n\n")

cat(paste0("There are ", length(unique(param_sum_au$AU_ID)), " assessment units within the ", name, " containing stations with available data for the parameters included in this report. Assessment units that did not contain stations with targets or sufficient available data are listed as unassessed. ", tbls(name = paste0(name, "_au_sum"), display = 'cite'), " shows the number of attaining, not attaining, and unassessed assessment units by parameter for the ", complete_years[17], "–", complete_years[20]," status period.\n\n"))

au_sum <- param_sum_au %>% dplyr::group_by(Char_Name) %>% 
  dplyr::summarise(Attaining = sum(status_2016_2019 == "Attaining"),
                   'Not Attaining' = sum(status_2016_2019 == "Not Attaining"),
                   Unassessed = sum(status_2016_2019 == "Unassessed")) %>% 
  dplyr::mutate(Char_Name = sapply(Char_Name, simpleCap, USE.NAMES = FALSE)) %>% 
  dplyr::rename(Pollutant = Char_Name)

knitr::kable(au_sum, padding = 0, digits = 1, row.names = FALSE, format = table_format,
             caption = tbls(name = paste0(name, "_au_sum"), caption = paste0("Summary of the ", complete_years[17], "–", complete_years[20]," assessment unit status within the ", name, "."))
) %>% table_style()

cat("\n\n")

ggplot2::ggplot(reshape2::melt(au_sum, id.vars = "Pollutant", variable.name = "Status"))+
  ggplot2::geom_bar(aes(x = Pollutant, y = value, fill = Status), stat = "identity", position = "dodge")+
  ggplot2::xlab("Pollutant")+
  ggplot2::ylab("# of Assessment Units")+
  ggplot2::scale_fill_manual(values = c("Attaining" = "forestgreen", "Not Attaining" = "orange", "Unassessed" = "gray"))+
  ggplot2::theme_bw()+
  ggplot2::ggtitle("Count of Assessment Unit Status", subtitle = "Summarized by Parameter")

cap_list[[1]] <- figs(name = paste0(name, "_au_sum_plot"), caption = paste0("The number of assessment units in each status category by parameter for the ", complete_years[17], "–", complete_years[20]," status period within the ", name, "."))

cat(paste0("\n\n",tbls(name = paste0(name, "_au_type_sum"), display = 'cite')," and ", figs(name = paste0(name, "_au_sum_plot"), display = 'cite')," summarizes the number of attaining, not attaining, and unassessed assessment units by parameter and assessment unit type within the ", name," for the ", complete_years[17], "–", complete_years[20]," status period.\n\n"))

au_sum_type <- param_sum_au %>% dplyr::group_by(AU_Type, Char_Name) %>% 
  dplyr::summarise(Attaining = sum(status_2016_2019 == "Attaining"),
                   "Not Attaining" = sum(status_2016_2019 == "Not Attaining"),
                   Unassessed = sum(status_2016_2019 == "Unassessed")) %>% 
  dplyr::mutate(Char_Name = sapply(Char_Name, simpleCap, USE.NAMES = FALSE)) %>% 
  dplyr::rename("AU Type" = AU_Type, Pollutant = Char_Name)

knitr::kable(au_sum_type, padding = 0, digits = 1, row.names = FALSE, format = table_format
             ,
             caption = tbls(name = paste0(name, "_au_type_sum"), caption = paste0("The number of assessment units in each status category by parameter for the ", complete_years[17], "–", complete_years[20]," status period within the ", name,"."))
) %>% table_style()


cat("\n\n")

cat(paste0("\n\n", tbls(name = paste0(name, "_stn_sum"), display = 'cite')," and ", figs(name = paste0(name, "_stn_sum_plot"), display = 'cite')," summarizes the number of attaining, not attaining, and unassessed stations by parameter for the ", complete_years[17], "–", complete_years[20]," status period. Stations without targets or without sufficient data to determine attainment are listed as unassessed. The reason for a station's unassessed status can be found in Appendix ", a.letter,"."))

stn_sum <- param_sum %>% dplyr::group_by(Pollutant) %>% 
  dplyr::summarise(Attaining = sum(status_2016_2019 == "Attaining"),
                   "Not Attaining" = sum(status_2016_2019 == "Not Attaining"),
                   Unassessed = sum(status_2016_2019 == "Unassessed")) %>% 
  dplyr::mutate(Pollutant = sapply(Pollutant, simpleCap, USE.NAMES = FALSE))

knitr::kable(stn_sum, padding = 0, digits = 1, row.names = FALSE, format = table_format
             ,
             caption = tbls(name = paste0(name, "_stn_sum"), caption = paste0("Summary of the ", complete_years[17], "–", complete_years[20]," status at monitoring stations within the ", name, "."))
) %>% table_style()

cat("\n\n")

ggplot2::ggplot(reshape2::melt(stn_sum, id.vars = "Pollutant", variable.name = "Status"))+
  ggplot2::geom_bar(aes(x = Pollutant, y = value, fill = Status), stat = "identity", position = "dodge")+
  ggplot2::xlab("Pollutant")+
  ggplot2::ylab("# of Stations")+
  ggplot2::scale_fill_manual(values = c("Attaining" = "forestgreen", "Not Attaining" = "orange", "Unassessed" = "gray"))+
  ggplot2::theme_bw()+
  ggplot2::ggtitle("Count of Monitoring Station Status", subtitle = "Summarized by Parameter")

cap_list[[2]] <- figs(name = paste0(name, "_stn_sum_plot"), caption = paste0("Summary plot of the ", complete_years[17], "–", complete_years[20]," station status within the ", name, " by parameter."))

cat("\n\n")
cat("### Trend\n\n")

cat(paste0("\n\nA summary of the trends across parameters is shown in ",tbls(name = paste0(name, "_stn_trend_sum"), display="cite"),". Note that trend requires significantly more data than status and may result in many stations with sufficient data for assessing status, but insufficient data for assessing trend.\n\n"))

stn_sum <- param_sum %>% dplyr::group_by(Pollutant) %>% 
  dplyr::summarise(Improving = sum(trend == "Improving"),
                   Degrading = sum(trend == "Degrading"),
                   Steady = sum(trend == "Steady"),
                   "No Significant Trend" = sum(trend == "No Significant Trend"),
                   "Insufficient Data" = sum(trend == "Insufficient Data"),
  ) %>% 
  dplyr::mutate(Pollutant = sapply(Pollutant, simpleCap, USE.NAMES = FALSE))

knitr::kable(stn_sum, padding = 0, digits = 1, row.names = FALSE, format = table_format
             ,
             caption = tbls(name = paste0(name, "_stn_trend_sum"), caption = paste0(name, " summary of trends at stations across the state."))
) %>% table_style()

cat("\n\n")

```

### Subbasin Summary

```{r subbasin, include = FALSE, eval=TRUE, results = 'asis'}

subbasin_output <- NULL

capnum <- 3

for(i in unique(param_sum$HUC8)){
  
  data <- param_sum %>% dplyr::filter(HUC8 == i)
  map_df <- data
  par_sum <- data %>% dplyr::select(-Lat_DD, -Long_DD, -HUC8, -HUC8_Name)
  par_sum_au <- param_sum_au %>% dplyr::filter(AU_ID %in% data$AU_ID)
  
  subbasin_name <- huc_names[huc_names$HUC8 == i,]$HUC8_Name
  sub_area <- area[area$HUC_8 == i,]
  sub_12s <- hucs[hucs$HUC_8 %in% i,]$HUC_12
  
  subbasin_output <- c(subbasin_output, knitr::knit_child("state_subbasin_summary.Rmd", envir = globalenv()))
  
  capnum <- as.numeric(capnum)
  
  print(capnum)
  
}

```

`r paste(subbasin_output, collapse = '\n')`
